A National Pipeline System as a Solution to Future Water Shortage in the United States

### 2013-02-04 paper.tex
change

@@

The first part of our analysis is a projection of future water needs. 
We used data from previous years to predict the amount of additional
water that each county will need by 2025. Creating such a projection is critical, as it informs us
of what kinds of infrastructure needs to be developed, and how significant of a problem water shortages are likely to occur in the forseeable future.

Our projections suggest that water shortages could indeed be a very significant problem leading up to 2025, in two significant ways:
On one hand, we predict that the overall water demand in the country will increase by several billion gallons per day, confined to several areas of substantial increase. We will attempt to solve this problem of total water supply by constructing additional 
de-salinization plants and reservoirs. We build these in the places that have the greatest predicted increase in their water demands.
The more significant problem however, as was the case in the drought of 2012-2013, is that even when there is enough water flowing in the United States as a whole, it might be the case that one city is flooding with water, while another is in drought.
We advise constructing a means of moving water on a large scale across the country, and this can be accomplished by constructing a network of high-volume pipelines.

>>>>

\begin{figure}[b]
        \centering
        \includegraphics[width=.85\textwidth]{graph}
\end{figure}

@@

The first part of our analysis is a projection of future water needs. 
We used data from previous years to predict the amount of additional
water that each county will need by 2025. Creating such a projection is critical, as it informs us
of what kinds of infrastructure need to be developed, and how significant of a problem water shortages are likely to become in the forseeable future.

Our projections suggest that water shortages could indeed be a very significant problem leading up to 2025, in two significant ways:
On one hand, we predict that the overall water demand in the country will increase by several billion gallons per day, confined to several areas of substantial increase. We will attempt to solve this problem of total water supply by constructing additional 
de-salinization plants and reservoirs. We build these in the places that have the greatest predicted increase in their water demands.
The more significant problem however, as was the case in the drought of 2012-2013, is that even when there is enough water available in the United States as a whole, it might be the case that while some regions are oversupplied, while others are severely in drought.
We advise constructing a means of moving water on a large scale across the country, and this can be accomplished by constructing a network of high-volume pipelines.
